---
title: "NeuroData: RORB synapse annotations"
author: "Jesse Leigh Patsolic"
date: Date `r Sys.Date()`
output: 
  html_document: 
    keep_md: yes
  pdf_document: default
---

<!--
### ### INITIAL COMMENTS HERE ###
###
### Jesse Leigh Patsolic 
### 2018 <jpatsolic@jhu.edu>
### S.D.G 
#
-->

```{r render, eval=FALSE, echo=FALSE}
## Run these lines to build the html file with Rmarkdown.
require(rmarkdown)
require(rjson)
require(data.table)
require(ggplot2)
require(latex2exp)
rmarkdown::render("Plot.Rmd", output_format = 'html_document')
system('open Plot.html')
```

# 16-bit data

## $K = $ Ones$(60, 60)$

```{r, echo = FALSE}
s <- file('synapse_results_16bit_k60.json', 'r')
ns <- file('nonSynapse_results_16bit_k60.json', 'r')

hs <- rjson::fromJSON(file = s)
hns <- rjson::fromJSON(file = ns)

close(s)
close(ns)

tmps <- Reduce(rbind, lapply(hs, function(x) Reduce(cbind, x)))
tmpns <- Reduce(rbind, lapply(hns, function(x) Reduce(cbind, x)))

colnames(tmps) <- names(hs[[1]])
colnames(tmpns) <- names(hns[[1]])
#
dats <- data.table(tmps)
datns <- data.table(tmpns)
```

> From: joshua vogelstein <jovo@jhu.edu> Mon, Oct 8, 2018 at 6:19 PM 
> To: Carey E Priebe <cep@jhu.edu>, Jesse Patsolic <studiojlp@gmail.com>, Benjamin Falk <falk.ben@jhu.edu>, joshua vogelstein <jovo@jhu.edu>
>
>cep - EM provides "gold standard" labels in images several different AT channels provide markers.
>somebody ran an algorithm, to detect synapses, and missed many.
>afaict, it would be literally impossible for any algorithm to detect them, because the "information content" is not there.
>the data are: (X_i,Y_i), i =1,...,n
>where Y_i is binary
>X_i natively lives in LxWxHxC space (or something close to it, a few voxels per plane, a few planes, and about 10 channels).
>we have ways that we like to reduce this to merely C, that is, the number of channels. we have ways to reduce C to 2.
>we have about 1000 Y_i=1 and can obtain, say, 1M Y_i=0.
>sometimes, however, when Y_i = 1, meaning the X_i's should be relatively large, they are zero.


> ..., it suggests the following analysis:
>centered at each centroid, just sum up all the voxels within a cube, call that t_i
>then, let's plot the fraction of detected synapses with t_i > t, and vary t from 0 to max t_i let's do that for each of the 2 "important channels", and/or all the channels.
>if the magnitude is not large enough, there is no function of the cube that could possibly detect the synapse.
> 

```{r datGather}
tsseq <- seq(0, max(dats$synapsin), by = 0.1)
tpseq <- seq(0, max(dats$psd), by = 0.1)

ntsseq <- seq(0, max(datns$synapsin), by = 0.1)
ntpseq <- seq(0, max(datns$psd), by = 0.1)

tSyn <- sapply(tsseq, function(x) sum(dats$synapsin > x) / nrow(dats))
tPSD <- sapply(tpseq, function(x) sum(dats$psd > x) / nrow(dats))

tnSyn <- sapply(ntsseq, function(x) sum(datns$synapsin > x) / nrow(datns))
tnPSD <- sapply(ntpseq, function(x) sum(datns$psd > x) / nrow(datns))
```


```{r, fig.height = 7, fig.width = 8, echo = FALSE}
plot(range(c(tsseq, tpseq)), range(c(tSyn, tPSD, tnSyn, tnPSD)), type = 'n')
points(tsseq, tSyn, type = 'l', xlab = 't', ylab = 't_i')
points(ntsseq, tnSyn, type = 'l', xlab = 't', ylab = 't_i', lty = 3, col = scales::alpha('black', 0.25))
points(tpseq, tPSD, type = 'l', col = 'red')
points(ntpseq, tnPSD, type = 'l', col = scales::alpha('red', 0.25), lty = 3)
text(quantile(tsseq, 0.25), 0.5, label = 'synapsin', col = 'black')
text(quantile(tsseq, 0.2), 0.6, label = 'psd95', col = 'red')
title("Fraction of t_i > t sweeping over t\n transparent lines are at 'non-synapses'.")
```

```{r newfig, fig.height = 9, fig.width = 9}
#tsseq <- seq(0, max(dats$synapsin), by = 0.1)
#tpseq <- seq(0, max(dats$psd), by = 0.1)
tseq <- seq(0, max(dats$psd, dats$synapsin), by = 0.1)
tSyn <- sapply(tseq, function(x) sum(dats$synapsin > x) / nrow(dats))
tPSD <- sapply(tseq, function(x) sum(dats$psd > x) / nrow(dats))
tSP <- sapply(tseq, function(x) sum((dats$psd + dats$syn) > x) / nrow(dats))


d1 <- data.frame(t = tseq, ti = tSyn, Channel = "synapsin")
d2 <- data.frame(t = tseq, ti = tPSD, Channel = "PSD95")
d3 <- data.frame(t = tseq, ti = tSP, Channel = "synapsin + PSD95")

ntseq <- seq(0, max(datns$psd, dats$synapsin), by = 0.1)
ntSyn <- sapply(ntseq, function(x) sum(datns$synapsin > x) / nrow(datns))
ntPSD <- sapply(ntseq, function(x) sum(datns$psd > x) / nrow(datns))
ntSP <- sapply(ntseq, function(x) sum((datns$psd + datns$syn) > x) / nrow(datns))

d4 <- data.frame(t = ntseq, ti = ntSyn, Channel = "synapsin")
d5 <- data.frame(t = ntseq, ti = ntPSD, Channel = "PSD95")
d6 <- data.frame(t = ntseq, ti = ntSP, Channel = "synapsin + PSD95")

d0s <- data.table(rbind(d1, d2, d3), type = 'synapse')
d0ns <- data.table(rbind(d4, d5, d6), type = 'non-synapse')

d0 <- data.table(rbind(d0s, d0ns))

ggplot(data = d0, aes(x = t, y = ti, group = Channel, col = Channel)) + 
  scale_y_continuous(breaks = seq(0, max(d0$ti), by = 0.1)) + 
  geom_line(alpha = 0.75) + 
  geom_vline(xintercept = 2.65, col = 'salmon', lty = 2) +  
  geom_vline(xintercept = 4.11, col = 'darkgreen', lty = 2) +  
  ylab(TeX("$t_i$")) + 
  facet_grid(type ~ .)

#ggplot(data = d0, aes(x = t, y = ti, group = Channel, col = Channel)) + 
#  scale_y_continuous(breaks = seq(0, max(d0$ti), by = 0.1)) + 
#  geom_line(alpha = 0.75) + 
#  geom_vline(xintercept = 2.65, col = 'salmon', lty = 2) +  
#  geom_vline(xintercept = 4.11, col = 'darkgreen', lty = 2) +  
#  ylab(TeX("$t_i$"))
#
#ggplot(data = d0n, aes(x = t, y = ti, group = Channel, col = Channel)) + 
#  scale_y_continuous(breaks = seq(0, max(d0$ti), by = 0.1)) + 
#  geom_line(alpha = 0.75) + 
#  geom_vline(xintercept = 2.65, col = 'salmon', lty = 2) +  
#  geom_vline(xintercept = 4.11, col = 'darkgreen', lty = 2) +  
#  ylab(TeX("$t_i$"))

```

```{r hist}
hist(dats$synapsin, prob = TRUE)
```



<!--
#   Time:
##  Working status:
### Comments:
####Soli Deo Gloria
--> 

