---
title: "NeuroData: RORB synapse annotations"
author: "Jesse Leigh Patsolic"
date: Date `r Sys.Date()`
output: 
  html_document: 
    keep_md: yes
  pdf_document: default
---

<!--
### ### INITIAL COMMENTS HERE ###
###
### Jesse Leigh Patsolic 
### 2018 <jpatsolic@jhu.edu>
### S.D.G 
#
-->

```{r render, eval=FALSE, echo=FALSE}
## Run these lines to build the html file with Rmarkdown.
require(rmarkdown)
require(rjson)
require(data.table)
require(ggplot2)
require(latex2exp)
rmarkdown::render("Plot.Rmd", output_format = 'all')
system('open Plot.html')
system('open Plot.pdf')
```

# 8-bit data

## $K = $ Ones$(30,30)$

```{r, echo = FALSE}
f <- file('results.json', 'r')
h <- rjson::fromJSON(file = f)
close(f)

tmp <- Reduce(rbind, lapply(h, function(x) Reduce(cbind, x)))

colnames(tmp) <- names(h[[1]])

dat <- data.table(tmp)
```

> From: joshua vogelstein <jovo@jhu.edu> Mon, Oct 8, 2018 at 6:19 PM 
> To: Carey E Priebe <cep@jhu.edu>, Jesse Patsolic <studiojlp@gmail.com>, Benjamin Falk <falk.ben@jhu.edu>, joshua vogelstein <jovo@jhu.edu>
>
>cep - EM provides "gold standard" labels in images several different AT channels provide markers.
>somebody ran an algorithm, to detect synapses, and missed many.
>afaict, it would be literally impossible for any algorithm to detect them, because the "information content" is not there.
>the data are: (X_i,Y_i), i =1,...,n
>where Y_i is binary
>X_i natively lives in LxWxHxC space (or something close to it, a few voxels per plane, a few planes, and about 10 channels).
>we have ways that we like to reduce this to merely C, that is, the number of channels. we have ways to reduce C to 2.
>we have about 1000 Y_i=1 and can obtain, say, 1M Y_i=0.
>sometimes, however, when Y_i = 1, meaning the X_i's should be relatively large, they are zero.


> ..., it suggests the following analysis:
>centered at each centroid, just sum up all the voxels within a cube, call that t_i
>then, let's plot the fraction of detected synapses with t_i > t, and vary t from 0 to max t_i let's do that for each of the 2 "important channels", and/or all the channels.
>if the magnitude is not large enough, there is no function of the cube that could possibly detect the synapse.
> 

```{r, fig.height = 5, fig.width = 7, echo = FALSE}
tsseq <- seq(0, max(dat$synapsin), by = 0.1)
tpseq <- seq(0, max(dat$psd), by = 0.1)

tSyn <- sapply(tsseq, function(x) sum(dat$synapsin > x) / nrow(dat))
tPSD <- sapply(tpseq, function(x) sum(dat$psd > x) / nrow(dat))

plot(tsseq, tSyn, type = 'l', xlab = 't', ylab = 't_i')
points(tpseq, tPSD, type = 'l', col = 'red')
text(quantile(tsseq, 0.25), 0.5, label = 'synapsin', col = 'black')
text(quantile(tsseq, 0.2), 0.6, label = 'psd95', col = 'red')
title("Fraction of t_i > t sweeping over t.")
```

```{r newfig}
#tsseq <- seq(0, max(dat$synapsin), by = 0.1)
#tpseq <- seq(0, max(dat$psd), by = 0.1)
tseq <- seq(0, max(dat$psd, dat$synapsin), by = 0.1)
tSyn <- sapply(tseq, function(x) sum(dat$synapsin > x) / nrow(dat))
tPSD <- sapply(tseq, function(x) sum(dat$psd > x) / nrow(dat))
tSP <- sapply(tseq, function(x) sum((dat$psd + dat$syn) > x) / nrow(dat))


d1 <- data.frame(t = tseq, ti = tSyn, Channel = "synapsin")
d2 <- data.frame(t = tseq, ti = tPSD, Channel = "PSD95")
d3 <- data.frame(t = tseq, ti = tSP, Channel = "synapsin + PSD95")

d0 <- rbind(d1, d2, d3)

ggplot(data = d0, aes(x = t, y = ti, group = Channel, col = Channel)) + 
  scale_y_continuous(breaks = seq(0, max(d0$ti), by = 0.1)) + 
  geom_line(alpha = 0.75) + 
  geom_vline(xintercept = 2.65, col = 'salmon', lty = 2) +  
  geom_vline(xintercept = 4.11, col = 'darkgreen', lty = 2) +  
  ylab(TeX("$t_i$"))

```

```{r hist}
hist(dat$synapsin, prob = TRUE)
```



<!--
#   Time:
##  Working status:
### Comments:
####Soli Deo Gloria
--> 

